### 2017-10-17 paper/sections/1_introduction.tex
paper: draft 1
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% What did we do
To address this problem, we present an API and framework that lets developers
dynamically control the consistency and durability guarantees for subtrees in
the file system namespace.  Figure~\ref{fig:subtree-policies} shows a setup in
our proposed system where a single global namespace has subtrees for
applications optimized with techniques from different state-of-the-art HPC
architectures.  The HDFS\footnote{This is example is not directly evaluated in
this paper, although a similiar use case is explored in~\S\ref{use-case-1}}
subtree has weaker consistency than strong consistency because it  does not
guarantee that all updates are not immediately seen by all servers; the BatchFS
and RAMDisk subtrees are decoupled from the global namespace and have similiar
consistency/durability behavior to those systems; and the POSIX subtree retains
the rigidity of POSIX's strong consistency.

Our protoype system, Cudele, achieves this by exposing ``mechanisms" that
developers use to specify their preferred semantics.  Cudele supports 3 forms
of consistency (invisible, weak, and strong) and 3 degrees of durability (none,
local, and global) giving the user a wide range of policies and optimizations
that can be custom fit to an application. We make the following contributions:

@@

% Results
Our results confirm the assertions of ``clean-state" research systems that
decouple namespaces; specifically that the technique drastically improves
performance (104\(\times\) speed up) but we go a step further by quantifying
the costs of merging updates (7\(\times\) slow down) and maintaining durability
(\(10\times\) slow down). We also show the effect of having a metadata specific
file format in systems that are based on in-memory data structures.  We scale
up to 20 clients executing an extremely metadata intensive job because this
workload exhausts the resources of a single metadata server for the codebase we
built on.  Partitioning and replicating metadata across a cluster can be
controlled with something like Mantle~\cite{sevilla:sc15-mantle}, but in this
paper we show the capacity and performance of a metadata server with superior
metadata protocols, which should be used to inform load balancing decisions.

>>>>

% What did we do
To address this problem, we present an API and framework that lets developers
dynamically control the consistency and durability guarantees for subtrees in
the file system namespace.  Figure~\ref{fig:subtree-policies} shows a setup in
our proposed system where a single global namespace has subtrees for
applications optimized with techniques from different state-of-the-art HPC
architectures.  The HDFS\footnote{This is example is not directly evaluated in
this paper, although a similar use case is explored in~\S\ref{use-case-1}}
subtree has weaker consistency than strong consistency because it  does not
guarantee that all updates are not immediately seen by all servers; the BatchFS
and RAMDisk subtrees are decoupled from the global namespace and have similar
consistency/durability behavior to those systems; and the POSIX subtree retains
the rigidity of POSIX's strong consistency.

Our prototype system, Cudele, achieves this by exposing ``mechanisms" that
developers use to specify their preferred semantics.  Cudele supports 3 forms
of consistency (invisible, weak, and strong) and 3 degrees of durability (none,
local, and global) giving the user a wide range of policies and optimizations
that can be custom fit to an application. We make the following contributions:

@@

% Results
Our results confirm the assertions of ``clean-state" research systems that
decouple namespaces; specifically that the technique drastically improves
performance (104\(\times\) speed up) but we go a step further by quantifying
the costs of merging updates (7\(\times\) slow down) and maintaining durability
(\(10\times\) slow down). We also show the effect of having a metadata specific
file format in systems that are based on in-memory data structures.  We scale
up to 20 clients executing an extremely metadata intensive job because this
workload exhausts the resources of a single metadata server for the code base we
built on.  Partitioning and replicating metadata across a cluster can be
controlled with something like Mantle~\cite{sevilla:sc15-mantle}, but in this
paper we show the capacity and performance of a metadata server with superior
metadata protocols, which should be used to inform load balancing decisions.

### 2017-10-17 paper/sections/3_posix_overheads.tex
paper: draft 1
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

In our examination of the overheads of POSIX we benchmark and analyze CephFS,
the file system that uses the Ceph's object store ({\it i.e.} RADOS) to store
its data and metadata. We choose CephFS because it is an open-source production
quality system. This file system is an implementation of one set of design
decisions and our goal is to highlight the effect that those decisions have on
performance. During this process we discovered, based on the analysis and
breakdown of costs, that durability and consistency have high overhead.

>>>>

% CITEME PDSW paper
In our examination of the overheads of POSIX we benchmark and analyze CephFS,
the file system that uses Ceph's object store ({\it i.e.} RADOS) to store its
data and metadata. Ceph was originally designed for HPC and has proven to be
useful for HPC workloads~\cite{}. Several features were motivated by HPC
requirements~\cite{weil:osdi2006-ceph}, so the lessons are useful (and can be
implemented) in HPC environments.  This file system is an implementation of one
set of design decisions and our goal is to highlight the effect that those
decisions have on performance. During this process we discovered, based on the
analysis and breakdown of costs, that durability and consistency have high
overhead.

### 2017-10-17 paper/sections/6_results.tex
paper: draft 1
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

We evaluate Cudele on a 15 node cluster, partitioned into 8 object storage
servers, 3 metadata servers, and 2 monitor servers. The object storage servers
double as clients which is fine because clients are CPU and memory bound while
object storage servers are disk IO bound. All daemons run as a single process
which is the default setting for Ceph and the nodes have 2 dual core 2GHz
processors with 8GB of RAM. There are three daemons per object storage server
(one for each disk formatted with XFS) and they share an SSD for the journal.
The nodes are running Ubuntu 12.04.4, kernel version 3.2.0-63 but all
experiments run in Docker containers; this makes it easier to tear down and
re-initialize the cluster ({\it e.g.}, dropping the kernel cache) between
experiments. For these experiments, we compare CephFS to our programmable
consistency and durability modifications, which we call Cudele.

>>>>

We did not compare to other HPC systems because we are not claiming that our
file system metadata protocols are superior. Instead, we use Ceph as a platform
for exploring related work over the same storage system, which facilitates an
apples-to-apples comparison of the strategies themselves.  So we run
experiments on the same cluster and normalize results to control for hardware
differences and to make our results more generally applicable.  Our goal is not
to build a file system optimized for HPC workloads and our prototype is not a
competitor to Lustre. Rather it is a solution for letting the techniques of a
system like Lustre live in the same namespace as techniques optimized for file
creates, like BatchFS.

We evaluate our prototype, which we call Cudele, on two clusters: a 15 node
in-house cluster with 1 monitor server, 1 metadata server, 8 object storage
servers, and 8 clients (co-located with object servers); and a 34 node CloudLab
cluster with 1 monitor server, 1 metadata server, 3 object storage servers, and
up to 29 clients. For the in-house cluster, We need more object storage servers
and we have to co-locate clients on the same node because of resource
contention \footnote{The bandwidth to RADOS is only sufficient with 8 nodes on
this older hardware, which uses SSDs and nodes that are almost 10 years old.
The CloudLab cluster performs just as well with and without a highly
provisioned object storage server cluster.}. All daemons run as a single
process which is the default setting for Ceph. We develop on Ceph's Jewel
release, version 10.2.1, which was released in May 2016.

%The in-house cluster has  2 dual core 2GHz processors with 8GB of RAM wh
%three daemons per object storage server (one for each disk formatted with XFS)
%and they share an SSD for the journal.  The nodes are running Ubuntu 12.04.4,
%kernel version 3.2.0-63 but all experiments run in Docker containers; this
%makes it easier to tear down and re-initialize the cluster ({\it e.g.},
%dropping the kernel cache) between experiments.
